Transferability of clinical prediction models for early trauma care

### 2019-09-18 ManuscriptMarkdown.Rmd
Update ManuscriptMarkdown.Rmd

---
title: "Transferability of clinical prediction models for early trauma care"
author: 
- Martin Henriksson
- Dell D Saulnier
- Johanna Berg
- Martin Gerdin Wärnberg
date: "September 09, 2019"
documentclass: "article"
output:
  word_document:
    reference_docx: transferstyle.docx
header-includes:
   - \usepackage{hyperref}
bibliography: library.bib
csl: bmcemerg.csl
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

@@

Table 2 shows the model validation performance. The model with the lowest validation
mistriage rate was the `r colnames(lowest.val.mistriage)` model, with a median
mistriage rate of `r lowest.val.mistriage`. The performance in terms of
undertriage and overtriage rate for the same model was `r val.undertriage` and
`r val.overtriage`, respectively. The worst validation performance (i.e. highest
mistriage rate) was found in the `r colnames(highest.val.mistriage)` sample, with
a model median mistriage rate of `r highest.val.mistriage`.

@@

## Comparison
Model performance after transfer was determined for each model after being transferred
to the other sample in the data set, in all data sets (Table 3). When
transferred, the model with the lowest mistriage rate was the `r colnames(lowest.tran.mistriage)` 
model, with a median mistriage rate of `r lowest.tran.mistriage`. The model with 
the highest mistriage rate after transfer was the `r colnames(highest.tran.mistriage)` model 
with a median mistriage rate of `r highest.tran.mistriage`.

@@

Table 4 shows the transferred model performance when compared to the validation
performance in the sample receiving the transferred model.
The highest mistriage rate when compared to the receiving sample validation
model performance was found in the `r colnames(highest.comp.mistriage)` model,
with a median mistriage rate difference of `r highest.comp.mistriage`, meaning
this model performed worse when transferred to the other sample in the same data
set. In clinical terms, this model transfer means that among 100 trauma
patients, `r abs(worst.transfer$Transferred.mistriage.minus.buddy.local.mistriage.median) * 100` 
more patients would be wrongly classified as having major or minor trauma.

>>>>

---
title: "Transferability of clinical prediction models for early trauma care"
author: 
- Martin Henriksson
- Dell D Saulnier
- Johanna Berg
- Martin Gerdin Wärnberg
date: "September 18, 2019"
documentclass: "article"
output:
  word_document:
    reference_docx: transferstyle.docx
header-includes:
   - \usepackage{hyperref}
bibliography: library.bib
csl: bmcemerg.csl
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

@@

Table 2 shows the model validation performance. The model with the lowest validation
mistriage rate was the `r colnames(lowest.val.mistriage)` model, with a median
mistriage rate of `r lowest.val.mistriage`. The performance in terms of
undertriage and overtriage rate for the same model was `r val.undertriage` and
`r val.overtriage`, respectively. The highest validation mistriage rate (i.e. worst
validation performance) was found in the `r colnames(highest.val.mistriage)` sample, with
a model median mistriage rate of `r highest.val.mistriage`.

@@

## Comparison
Model performance after transfer was determined for each model after being transferred
to the validation subsample in the other sample, in the data set (Table 3). When
transferred, the model with the lowest mistriage rate was the `r colnames(lowest.tran.mistriage)` 
model, with a median mistriage rate of `r lowest.tran.mistriage`. The model with 
the highest mistriage rate after transfer was the `r colnames(highest.tran.mistriage)` model 
with a median mistriage rate of `r highest.tran.mistriage`.

@@

Table 4 shows the transferred model performance when compared to the validation
performance in the validation subsample receiving the transferred model.
The highest mistriage rate when compared to the receiving sample validation
model performance was found in the `r colnames(highest.comp.mistriage)` model,
with a median mistriage rate difference of `r highest.comp.mistriage`, meaning
this model performed worse when transferred to the other sample in the same data
set. In clinical terms, this model transfer means that among 100 trauma
patients, `r abs(worst.transfer$Transferred.mistriage.minus.buddy.local.mistriage.median) * 100` 
more patients would be wrongly classified as having major or minor trauma.
